\begin{thebibliography}{00}

    % --- Источники на русском ---

    \bibitem{web_scrapping}\hypertarget{web_scrapping}{}
    Веб-скрейпинг. — Текст : электронный // Википедия : свободная энциклопедия. — URL: \href{https://ru.wikipedia.org/wiki/Веб-скрейпинг}{https://ru.wikipedia.org/wiki/Веб-скрейпинг} (дата обращения: 26.04.2026).

    \bibitem{omnichannel_def}\hypertarget{omnichannel_def}{}
    Омниканальность. — Текст : электронный // Wikipedia : [сайт]. — URL: \href{https://ru.wikipedia.org/wiki/Омниканальность}{https://ru.wikipedia.org/wiki/Омниканальность} (дата обращения: 25.04.2026).

    % --- Источники на английском ---

    \bibitem{b4}
    Ali, M. A. Building Microservices with FastAPI / M. A. Ali. — Birmingham : Packt Publishing, 2023. — TODO p. — Текст : непосредственный.

    \bibitem{kafka_def}
    Apache Kafka: обработка потоков данных в реальном времени. — Текст : электронный // Yandex Cloud : [сайт]. — URL: \url{https://yandex.cloud/ru/blog/apache-kafka-overview} (дата обращения: 26.04.2026).

    \bibitem{b8}
    Brazil, B. Prometheus: Up \& Running: Infrastructure and Application Performance Monitoring / B. Brazil. — Sebastopol : O'Reilly Media, 2018. — TODO p. — Текст : непосредственный.

    \bibitem{red_def}
    Dam, Julie The RED Method: How to Instrument Your Services / Julie Dam. — Текст : электронный // GrafanaLabs : [сайт]. — URL: \url{https://grafana.com/blog/the-red-method-how-to-instrument-your-services/} (дата обращения: 26.04.2026).

    \bibitem{b2}
    Docker: Elevated Container Application Development. — Текст : электронный // Docker : [сайт]. — 2024. — URL: \url{https://www.docker.com/} (дата обращения: 15.05.2024).

    \bibitem{fomo_def}
    Fear of missing out. — Текст : электронный // Wikipedia : [сайт]. — URL: \url{https://en.wikipedia.org/wiki/Fear_of_missing_out} (дата обращения: 26.04.2026).

    \bibitem{api_def}\hypertarget{api_def}{}
    Goodwin, Michael. What is an API (application programming interface)? / Michael Goodwin. — Текст : электронный // IBM : [сайт]. — URL: \url{https://www.ibm.com/think/topics/api} (дата обращения: 26.04.2026).

    \bibitem{grafana_official}\hypertarget{grafana_official}{}
    Grafana support for Prometheus. — Текст : электронный // prometheus.io : [сайт]. — URL: \url{https://prometheus.io/docs/visualization/grafana/} (дата обращения: 23.04.2026).

    \bibitem{hauss2020}
    Hauss,~K. What are the social and scientific benefits of participating at academic conferences? Insights from a survey among doctoral students and postdocs in Germany~/ K.~Hauss~// Research Evaluation.~--- 2020.~--- P.~4--9.~--- DOI:~10.1093/reseval/rvaa018.~--- URL: \url{https://pmc.ncbi.nlm.nih.gov/articles/PMC7499794/} (дата обращения: 26.05.2024).

    \bibitem{http_def}
    HTTP. — Текст : электронный // Wikipedia : [сайт]. — URL: \url{https://ru.wikipedia.org/wiki/HTTP} (дата обращения: 26.04.2026).

    \bibitem{jwt}\hypertarget{jwt}{}
    JSON Web Token (JWT). — Текст : электронный // Yandex Cloud : [сайт]. — URL: \url{https://yandex.cloud/ru/docs/glossary/jwt} (дата обращения: 26.04.2026).

    \bibitem{attending_conferences_benefits}
    Marilena, D. N. Benefits of Attending Conferences for Career Advancement / D. N. Marilena. — Текст : электронный // Momentive Software : [сайт]. — URL: \url{https://momentivesoftware.com/blog/benefits-of-attending-conferences/}. (дата обращения: 25.04.2026).

    \bibitem{b1}
    Mitchell, R. Web Scraping with Python: Collecting More Data from the Modern Web / R. Mitchell. — 2nd ed. — Sebastopol : O'Reilly Media, 2018. — TODO p. — Текст : непосредственный.

    \bibitem{b9}
    Nygard, M. T. Release It!: Design and Deploy Production-Ready Software / M. T. Nygard. — 2nd ed. — Raleigh : Pragmatic Bookshelf, 2018. — TODO p. — Текст : непосредственный.

    \bibitem{b3}
    Obe, R. O. PostgreSQL: Up and Running / R. O. Obe, L. S. Hsu. — 3rd ed. — Sebastopol : O'Reilly Media, 2017. — TODO p. — Текст : непосредственный.

    \bibitem{openapi_def}
    OpenAPI. — Текст : электронный // Yandex Cloud : [сайт]. — URL: \url{https://yandex.cloud/ru/docs/glossary/openapi} (дата обращения: 26.04.2026).

    \bibitem{b5}
    Percival, H. Architecture Patterns with Python: Enabling Test-Driven Development, Domain-Driven Design, and Event-Driven Microservices / H. Percival, B. Gregory. — Sebastopol : O'Reilly Media, 2020. — TODO p. — Текст : непосредственный.

    \bibitem{rest_api_def}
    REST API: для чего нужен и как работает. — Текст : электронный // Yandex Cloud : [сайт]. — URL: \url{https://yandex.cloud/ru/docs/glossary/rest-api} (дата обращения: 26.04.2026).

    \bibitem{b7}
    Shapira, G. Kafka: The Definitive Guide: Real-Time Data and Stream Processing at Scale / G. Shapira, T. Palino, R. Sivaram, K. Pramod. — 2nd ed. — Sebastopol : O'Reilly Media, 2021. — TODO p. — Текст : непосредственный.

    \bibitem{prometheus_guide}\hypertarget{prometheus_guide}{}
    schkn Prometheus Monitoring : The Definitive Guide in 2019 / schkn. — Текст : электронный // devconnected.com : [сайт]. — URL: \url{https://devconnected.com/the-definitive-guide-to-prometheus-in-2019/} (дата обращения: 26.04.2026).

    \bibitem{grafana_guide}\hypertarget{grafana_guide}{}
    schkn How To Create a Grafana Dashboard? (UI + API methods) / schkn. — Текст : электронный // devconnected.com : [сайт]. — URL: \url{https://devconnected.com/how-to-create-a-grafana-dashboard-ui-api-methods/} (дата обращения: 26.04.2026).

    \bibitem{smtp_def}
    Simple Mail Transfer Protocol. — Текст : электронный // Wikipedia : [сайт]. — URL: \url{https://en.wikipedia.org/wiki/Simple_Mail_Transfer_Protocol} (дата обращения: 26.04.2026).

    \bibitem{prometheus_official}\hypertarget{prometheus_official}{}
    What is Prometheus?. — Текст : электронный // prometheus.io : [сайт]. — URL: https://prometheus.io/docs/introduction/overview/ (дата обращения: 23.04.2026).

\end{thebibliography}
